One-shot learning: From domain knowledge to action models

### 2019-02-25 doc/ijcai-19-deductivelearning/deductivelearning.tex
Submission number

@@

Table \ref{tab:observability_vs_knowledge} shows the average precision (P) and recall (R) for each domain in the four tested settings. The table also reports the number of schematic mutexes ($|\Phi|$) used for each domain. Comparing the settings \emph{only domain knowledge} (setting 2) with \emph{only observability} (setting 3), we can see that slightly better results are obtained with the latter, meaning that observability is slightly more informative than domain knowledge. On the other hand, the gain of using $\Phi$ under minimal observability (setting 1 compared to setting 2) is rather marginal. While these results might indicate a general preference for observations over knowledge, when comparing setting 3 with setting 4, we can observe a significant improvement in the quality of the learned models. This indicates that the payoff of using $\Phi$ is noticeable when the learning example has a certain degree of observability.

@@

We present an approach to learn action models that builds upon a former compilation-to-planning learning system~\cite{aineto2018learning}. Our proposal studies the gains of using domain-specific knowledge at the cost of limiting the learning examples to the minimal observability possible. Introducing domain knowledge encoded as schematic mutexes allows to narrow down the search space of the learning task and improve overall the performance of the learning system to the point that it offsets the lack of learning examples.

>>>>

\author{\#2922}

@@

Table \ref{tab:observability_vs_knowledge} shows the average precision (P) and recall (R) for each domain across the 10 learning examples in the four tested settings. The table also reports the number of schematic mutexes ($|\Phi|$) used for each domain. Comparing the settings \emph{only domain knowledge} (setting 2) with \emph{only observability} (setting 3), we can see that slightly better results are obtained with the latter, meaning that observability is slightly more informative than domain knowledge. On the other hand, the gain of using $\Phi$ under minimal observability (setting 1 compared to setting 2) is rather marginal. While these results might indicate a general preference for observations over knowledge, when comparing setting 3 with setting 4, we can observe a significant improvement in the quality of the learned models. This indicates that the payoff of using $\Phi$ is noticeable when the learning example has a certain degree of observability.

@@

We present an approach to learn action models that builds upon a former compilation-to-planning learning system~\cite{aineto2018learning}. Our proposal studies the gains of using domain-specific knowledge when the availability of learning examples is very limited. Introducing domain knowledge encoded as schematic mutexes allows to narrow down the search space of the learning task and improve overall the performance of the learning system to the point that it offsets the lack of learning examples.
